

```{r}
#| label: setup
#| include: false

library(knitr)
```

# Code and tables

## Syntax highlighting

Here is a sample code chunk, just to show that syntax highlighting works as expected as well as code annotations.

```{r}
#| label: sh
#| echo: true
#| eval: true
say_hello <- function(name) {
    paste("Hello,", name, "!") # <1>
}

say_hello("world") # <2>
```
1. Quite an original example.
2. This is were all the action is happening.

## Verbatim

Here is the structure of the `penguins` dataset.

```{r}
#| label: penguins_str
#| echo: true
#| code-line-numbers: true
library(palmerpenguins)
str(penguins)
```

## Tables

Sample table output.

```{r}
#| label: table
tab <- table(penguins$island, penguins$species)
kable(tab)
```

Sample `DT:datatable` output.

```{r}
#| label: dt
library(DT)
DT::datatable(penguins)
```


# Styling

A simple list : 

- one mississipi
- two mississipi
- three mississipi


A blockquote :

> Oh ! What a nice blockquote you have here. Much more wonderful than a classical lorem ipsum, really.

And we could also [include links](https://www.r-project.org/) or simply URLs like this : <https://www.r-project.org/>^[And even footnotes].

An incredibly complex equation :

$$ y = \sqrt{\frac{1}{x + \beta}} $$


# Figures

Here is an histogram.

```{r}
#| label: hist
library(ggplot2)
ggplot(data = penguins) +
    geom_histogram(aes(x = body_mass_g)) +
    facet_grid(rows = vars(species))
```

And a wonderful scatterplot, with a caption.

```{r}
#| label: scatter
#| fig.cap: "This is a scatterplot"
ggplot(data = penguins) +
    geom_point(
        aes(x = bill_length_mm, y = bill_depth_mm)
    )
```


# Callouts

::: {.callout-note}
This is a note callout.
:::

::: {.callout-warning}
This is a warning callout
:::

::: {.callout-important}
This is an important callout
:::

::: {.callout-caution}
This is a caution callout
:::

::: {.callout-tip}
This is a tip callout.With a bit of `code`.
:::

# Tabset

:::{.panel-tabset}

## First tab

This is the first tab content.

## Second tab

This is the second tab content.

:::