# Features overview

This is a book created from markdown and executable code.

See @knuth84 for additional discussion of literate programming.

```{r}
#| label: setup
#| include: false

library(knitr)
```

## Code and tables

### Syntax highlighting


Here is a sample code chunk^[With a footnote], just to show that syntax highlighting works as expected.

```{r}
#| label: sh
#| echo: true
#| eval: true
say_hello <- function(name) {
    paste("Hello,", name, "!")
}

say_hello("world")
```


### Verbatim


Here is the structure of the `penguins` dataset.

```{r}
#| label: penguins_str
#| echo: true
library(palmerpenguins)
str(penguins)
```

### Table


Sample table output.

```{r}
#| label: table
tab <- table(penguins$island, penguins$species)
kable(tab)
```

Sample `DT:datatable` output.

```{r}
#| label: dt
library(DT)
DT::datatable(penguins)
```


## Styling

A simple list : 

- one mississipi
- two mississipi
- three mississipi


A blockquote :

> Oh ! What a nice blockquote you have here. Much more wonderful than a classical Lorem Ipsum, really.

And we could also [include links](https://www.r-project.org/) or simply URLs like this : https://www.r-project.org/

An incredibly complex equation :

$$ y = \sqrt{\frac{1}{x + \beta}} $$


## Figures

Here is an histogram.

```{r}
#| label: hist
library(ggplot2)
ggplot(data = penguins) +
    geom_histogram(aes(x = body_mass_g)) +
    facet_grid(species ~ .)

```

And a wonderful scatterplot, with a caption.

```{r}
#| label: scatter
#| fig.cap: "This is a scatterplot"
ggplot(data = penguins) +
    geom_point(aes(x = bill_length_mm, y = bill_depth_mm))
```



### Callouts


::: {.callout-note}
This is a note callout
:::

::: {.callout-warning}
This is a warning callout
:::

::: {.callout-important}
This is an important callout
:::

::: {.callout-caution}
This is a caution callout
:::

::: {.callout-tip}
This is a tip callout
:::
